Outflows and rotation in Lyman alpha emitting galaxies

### 2017-04-07 paper/paper.tex
estructura de los resultados

In Table \ref{tab:values} we list the combination of $\tau_{\rm{H}}$,
$v_{rot}$ and $v_{out}$ values used in this paper.
The range of values have some overlap with the expectations from a dwarf
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$ $M_{\odot}$.
We run a total of $21$ different models.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      $\tau_{\mathrm{H}}$ & $v_{rot}$ (\kms) & $v_{out}$ (\kms) \\
      \hline
      $10^5$  & \{0, 50, 100\} & \{25, 50\} \\
      $10^6$ & \{0, 50, 100\} & \{25, 50\}\\
      $10^7$ & \{0, 50\} & \{25, 50\}\\
      $10^7$ & \{0, 100\} & \{50, 100, 200\}\\
      \hline    
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    $\tau_{\rm{H}}$,
    $v_{rot}$ and $v_{out}$ are used.}
  \label{tab:values}
\end{table}

@@

@@

These 3 parameters, vrot, vout and tauh, leave the idea of a model of
LAE, that although simple, considers the main galaxy's dynamics. All
of them have been previously proposed and used by different authors,
but never combined together (\cite{Adams72}, \cite{Harrington73}, \cit
e{Neufeld90}, \cite{Dijkstra06}, \cite{Verhamme06}, \cite{Forero12},
\cite{Martin2015}, \cite{Garavito14}, \cite{Neufeld91},
\cite{Laursen09}, \cite{Barnes11}, \cite{Verhamme12},
\cite{Yajima12}).\\

%mirar donde pongo esto
However, in the plots shown in this paper we use instead velocity,
$V$, units. This eases the comparison against observational data. The
velocity units are defined by 
The units of $V$ are usually \kms. In this case, the photon is
redshifted in frequency when the velocity is greater than 0, and
blueshifted in the opposite case. \\

The initial emission of photons is taken at the center of the sphere
for practicality due to the fact that both, center and off-center
emissions, give analogous results. From here, $100000$ photons are
emitted with the natural \lya wavelength and start to scatter. When
each photon is re-emitted, its new wavelength depends on the H atom's
velocity (both thermal and bulk) and direction (both initial and
final). However the photon's new direction of propagation is random in
the rest frame of the atom. \\

The individual scattering of all the photons is tracked through the
complete 3D Hydrogen distribution. Once each photon escapes the
galaxy, its final values are stored: position $\vec{r}$, direction of
propagation $\hat{k}$, dimensionless frequency $x$, and number of
scatterings $N$. To build the observed spectrum we make a histogram of
the escape frequencies $x$. The number of scatterings $N$ tells how
many steps the random walk requires to reach a distance to the center
that is $\geq R$. In order to avoid situations in which the photon has
not escaped after a long computational time, CLARA defines a number
$N_{max}$ so the code stops. However, according to statistics, this
last situation has low probabilities, so the photon is always most
likely to exit the sphere. \\

%The process that takes place from the moment the first photon is emitted to the moment the last photon escapes the sphere, is called a simulation. Each simulation runs in the scientific computational cluster of Universidad de los Andes due to the computing resources it requires. Depending on tauh, we need a different number of processors in order to minimize the time demands. For tauh $=10^5, 10^6, 10^7$ we use 6, 12, 24 processors, respectively. The running times go from 7 hours to 1 week approximately, depending on the case. \\

\subsection{Galaxy's Viewing Angle}
An observer located far away, only receives photons emitted along its
line of sight. That means, only photons escaping in the direction of
the observer must be counted in the spectrum. In the simulation we
approximate this by taking into account only the photons with escaping
direction angle $\theta$ respect to the rotation axis within the range
$[\theta_{min}-\theta_{max}]$.

@@

Therefore, in principle the spectra depend on two new parameters, the azimuthal and the polar angle. However, the galaxy's motion is symmetrical respect to its rotation axis. This implies that the resulting spectrum is independent from the azimuthal angle. Taking into account this symmetry, we only select photons on their polar angle, regardless of their azimuthal angle. Regarding the polar angle, we build the spectra for observers located on 3 different positions, with $\theta$ intervals uniformly distributed in $\cos(\theta)$. \\

To summarize, the parameters influencing the spectra are vrot, vout, tauh and $\theta$. In the next section we evaluate the impact each of these has on the resulting profile. \\

>>>>

In Table \ref{tab:values} we list the combination of $\tau_{\rm{H}}$,
$v_{rot}$ and $v_{out}$ values used in this paper.
The range of values have some overlap with the expectations from a dwarf
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$ $M_{\odot}$.
We run a total of $24$ different models.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      $\tau_{\mathrm{H}}$ & $v_{rot}$ (\kms) & $v_{out}$ (\kms) \\
      \hline
      $10^5$  & \{0\} & \{5, 25, 50\} \\
      $10^6$ & \{0\} & \{5, 25, 50\}\\
      $10^7$ & \{0\} & \{5, 25, 50\}\\
      $10^5$  & \{50, 100\} & \{25, 50, 75\} \\
      $10^6$ & \{50, 100\} & \{25, 50,75\}\\
      $10^7$ & \{50, 100\} & \{25, 50,75\}\\
      \hline    
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    $\tau_{\rm{H}}$,
    $v_{rot}$ and $v_{out}$ are used.}
  \label{tab:values}
\end{table}

@@

We evaluate first the effects of increasing rotational
velocity at fixed values of the optical depth and outflow velocity.
Figure \ref{fig:varying_rotation} summarizes the information.
All plots correspond to the same outflow velocity of $v_{out}=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

% Esta figura deberia tener 3 x 3 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vrot=0, | tau=1E5, vrot=50, | tau=1E5, vrot=100, 
% |tau=1E6, vrot=0, | tau=1E6, vrot=50, | tau=1E6, vrot=100, 
% |tau=1E7, vrot=0, | tau=1E7, vrot=50, | tau=1E7, vrot=100,

We now evaluate the effects of increasing outflow velocity at fixed
values for the optical depth and rotational velocity.
Figure \ref{fig:varying_outflow} summarizes the information following
the same patters as Figure \ref{fig:varying_rotation}, only that this
time all plots correspond to the same rotation velocity of
$v_{rot}=50$\kms,

% Esta figura deberia tener 3 x 3 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vout=25, | tau=1E5, vout=50, | tau=1E5, vout=75,
% |tau=1E6, vout=25, | tau=1E6, vout=50, | tau=1E6, vout=75,
% |tau=1E7, vout=25, | tau=1E7, vout=50, | tau=1E7, vout=75,

@@

(\cite{Adams72}, \cite{Harrington73}, \cit
e{Neufeld90}, \cite{Dijkstra06}, \cite{Verhamme06}, \cite{Forero12},
\cite{Martin2015}, \cite{Garavito14}, \cite{Neufeld91},
\cite{Laursen09}, \cite{Barnes11}, \cite{Verhamme12},
\cite{Yajima12}).\\

\subsection{Galaxy's Viewing Angle}

@@
